Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-01 paper.qmd
Added Figure 10 all projections

@@

@@

```{r}
#| fig-cap: "Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal."
#| fig-height: 15
#| fig-width: 15

free(distance_hist) / wrap_plots(trimesh_two_curvy2, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1, two_curvy_proj_umap_model, ncol = 3) 
```

>>>>

## Projection with Delauany triangulation

model_df1 <- dplyr::left_join(
  distance_two_curvy |> select(-distance), 
  projected_model_df, 
  by = c("from" = "ID"))

names(model_df1)[3:NCOL(model_df1)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_from")

model_df1 <- dplyr::left_join(model_df1, projected_model_df, by = c("to" = "ID"))
names(model_df1)[(2 + NCOL(projected_model_df)):NCOL(model_df1)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_to")

## With benchmark option 2

model_df2 <- dplyr::left_join(
  distance_df_small_edges_two_curvy3 |> select(-distance), 
  projected_model_df, 
  by = c("from" = "ID"))

names(model_df2)[3:NCOL(model_df2)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_from")

model_df2 <- dplyr::left_join(model_df2, projected_model_df, by = c("to" = "ID"))
names(model_df2)[(2 + NCOL(projected_model_df)):NCOL(model_df2)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_to")

@@

two_curvy_proj_umap_model_delaunay <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df1, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("c") +
  theme(
    legend.position = "none"
  )

two_curvy_proj_umap_model_benchmark2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df2, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("c") +
  theme(
    legend.position = "none"
  )

@@

```{r}
#| fig-cap: "Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal: (b) benchmark = 2$a_1$ and (c) benchmark = 5$a_1$, where $a_1$ = 0.09."
#| fig-height: 15
#| fig-width: 15

free(distance_hist) / wrap_plots(trimesh_two_curvy2, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1,
two_curvy_proj_umap_model_delaunay,
two_curvy_proj_umap_model_benchmark2,
two_curvy_proj_umap_model, ncol = 3) 
```
